Quality Assesment of OpenStreetMap Footpath Data for 3D City Recreation

### 2020-05-27 report/report.tex
Implementation summary

>>>>

In section 4.1 we will look at the data collection process for the geodata precision study. We will look at how to qualify dataset completeness and building correspondence (how many of the buildings in one dataset that can be found in the other) by collecting the cumulative building areas and looking at what buildings have overlapping areas between the two datasets.
We will also look at the difinitions and algorithms neccessary for calculating posiitonal accuracy and a measure for shape accuracy.
In section 4.2 we will look at the data collection process for the collision study. We will look at the how standard road withs were obtained, as well as the algorithm for detemining feature collision that was used.
In section 4.3 we will discuss briefly the data sources used in this project, why they were chosen and specific issues with the data collection process.
